Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-06-06 paper.tex
Update on Overleaf.

Unikernels present an ideal surface for prototyping Rust. Unikernels are designed to do one thing
and one thing only, thus limiting the complexity that a general-purpose operating system has to
deal with. This reduced complexity was explored by Lankes et al.~\cite{Lankes2019-cm}. The authors
detailed their experiences with rewriting an existing Unikernel, HermitCore, in Rust. The new
Unikernel named RustyHermit consists of only 3.27\% unsafe Rust, with the rest
of the code base consisting of safe Rust, dramatically decreasing the surface area where memory errors
could originate.

@@

Comparing performance, throughput and latency between different systems with different architectures is very difficult. For
example, several of the operating systems written in Rust are a complete rethinking of
how an operating system is designed~\cite{Boos2020-zh} while others run entirely in kernel space~\cite{Lankes2019-cm}. Additionally, direct comparisons between a Monolithic kernel, Micro-kernel, and Unikernel, or
comparisons between a Real Time Operation System (RTOS) and a General Purpose Operating System, are
not directly meaningful due to the vastly different goals of each system and the overhead that is imposed by the hardware~\cite{{Arnott2012-fl}. Therefore, we will focus
more on the overall efforts that are specific to the Rust programming language and the challenges
presented. We summarize our findings in table~\ref{tab:RQ2}.

Culic et al.~\cite{Culic2022-bk} looked at latency issues in the Tock OS. Tock is a new operating
system that is designed to run on embedded systems but does not provide Real-time capabilities. The
authors attempted to add real-time capabilities by integrating eBPF into the Tock kernel to improve
the interrupt handler's response time. The Authors found that early work (still in the prototype
stage) lowers the response times of the system and interrupts response times 3x.

>>>>

Unikernels present an ideal surface for prototyping Rust~\cite{Madhavapeddy2014-zw}. Unikernels are designed to do one thing
and one thing only, thus limiting the complexity that a general-purpose operating system has to
deal with. This reduced complexity was explored by Lankes et al.~\cite{Lankes2019-cm}. The authors
detailed their experiences with rewriting an existing Unikernel, HermitCore, in Rust. The new
Unikernel named RustyHermit consists of only 3.27\% unsafe Rust, with the rest
of the code base consisting of safe Rust, dramatically decreasing the surface area where memory errors
could originate.

@@

Comparing performance, throughput and latency between different systems with different architectures is very difficult. For
example, several of the operating systems written in Rust are a complete rethinking of
how an operating system is designed~\cite{Boos2020-zh} while others run entirely in kernel space~\cite{Lankes2019-cm}. Additionally, direct comparisons between a Monolithic kernel, Micro-kernel, and Unikernel, or
comparisons between a Real Time Operation System (RTOS) and a General Purpose Operating System, are
not directly meaningful due to the vastly different goals of each system and the overhead that is imposed by the hardware~\cite{Arnott2012-fl}. Therefore, we will focus more on the overall efforts that are specific to the Rust programming language and the challenges
presented. We summarize our findings in table~\ref{tab:RQ2}.

Culic et al.~\cite{Culic2022-bk} looked at latency issues in Tock. Tock is a new operating
system written in Rust that is designed to run on embedded systems but does not provide Real-time capabilities. The
authors attempted to add real-time capabilities by integrating eBPF into the Tock kernel to improve
the interrupt handler's response time. The Authors found that early work (still in the prototype
stage) lowers the response times of the system and interrupts response times 3x.
